Automated data-driven symbolic modeling of the lift forces acting on flapping wings

### 2021-02-07 paper/main.tex
Edit evaluation of model performance section

Table~\ref{table:eqmodels} shows the size of all equations considered in this
study, and indicates that the analytical models are all significantly more
complex than our data-driven models.  One of the reasons for high complexity in
the analytical models is the dependence on wing geometry and integration of
forces over the span and chord of the wing.  A second reason for the complexity
in analytical models is the number of geometric and coordinate transformations
required to compute the necessary linear and rotational velocities.  In this
sense, several terms generated during symbolic regression can be considered to
be approximations of much more subtle calculations of kinematic quantities.

The accuracy of each equation was measured as the mean absolute error (MAE)
between the predicted and actual vertical force (in Newtons) produced by the
flapping wing.  Figure~\ref{fig:pareto_mae} shows the Pareto plot of all models
considered, depicting accuracy as a function of model complexity. It is
important to note that all data-driven models have between three and five
coefficients, so tuning these coefficients allows further minimization of error
compared to the analytical models, which have between one and three.
Nevertheless, discovery of models with smaller error than theoretical
predictions that are simultaneously much simpler is a significant feat for the
data mining process and symbolic regression.

>>>>

Table~\ref{table:eqmodels} shows the size of all equations considered in this
study, and indicates that the analytical models are all significantly more
complex than our data-driven models.  Figure~\ref{fig:pareto_mae} illustrates
model accuracy as a function of complexity.  One of the reasons for high
complexity in the analytical models is the dependence on wing geometry and
integration of forces over the span and chord of the wing.  A second reason for
the complexity in analytical models is the number of geometric and coordinate
transformations required to compute the necessary linear and rotational
velocities.  In this sense, several terms generated during symbolic regression
can be considered to be approximations of much more subtle calculations of
kinematic quantities. Nevertheless, discovery of models with smaller error than
theoretical predictions that are simultaneously much simpler is a significant
feat for the data mining process and symbolic regression.
